Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-21 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:21	15:51:54	(Fri21.Aug)

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

@@

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

\section{Results and Discussion}

@@

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{Window parameter boundaries. LCA images using an oversampled image and a relatively large window database with $N_\beta=20$ window types, each steered $N_\phi=19$. }\label{oversampling_mosaic_bounds_beta}
\end{figure*}

@@

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}

@@

\todopar{Threw some formulas in to get a feel of them}

>>>>

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.eps}%
\caption{Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

@@

\begin{figure*}[t]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.eps}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The responses are overlayed each other. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.eps}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds_beta}
\end{figure*}

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.eps}%
\caption{Window parameter boundaries. LCA images using an oversampled image and a relatively large window database with $N_\beta=20$ window types, each steered $N_\phi=19$. }\label{oversampling_mosaic_bounds}
\end{figure*}

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic.eps}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic}
\end{figure*}

\newpage
\section{Results and Discussion}

@@

@@

@@

% \todopar{Threw some formulas in to get a feel of them}
